Disturbance-aware minimum-time planning strategies for motorsport vehicles with probabilistic safety certificates

### 2025-04-03 stochastic_vehicle_dynamics.tex
[MGa] basic structure

\section{Closed-loop uncertainty-aware planning over the full horizon}
\label{sec:closed_loop_planning}

Building upon our previous paper that presented a 3D multibody model suitable for embedding within an MLTP problem~\cite{Domenighini:Designs:2023} - treated here as the \emph{baseline} model - two models with increasing complexity are presented. The first represents a vehicle capable of independently steering all four wheels (AS) and applying four independent torques to each wheel (AIWD, aka, torque vectoring), whereas the second model additionally incorporates an active camber variation system for each wheel (DCC).
%The kinematic tree of the two models is slightly different, but the procedure used to build the dynamic model is similar apart from a non-trivial aspect that will be discussed later on. In the remainder of this study, unless otherwise specified, the descriptions provided apply to both models. The figures related to Sections~\ref{sec:suspanal}-\ref{sec:tyremodel} are courtesy of the authors.

>>>>

\section{Stochastic vehicle dynamics}
\label{sec:stochastic_vehicle_dynamics}

Some text of a previous paper left for reference on equation and pseudo-code formatting.
